---
title: "quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette gives a basic example of how to use the `fars` package.

```{r setup}
library(fars)
```

To be able to read the files, they need to be provided in the following format
`accident_2013.csv.bz2`, this format can be provided with the utility function
`make_filename` as follows:

```{r}
filename <- make_filename("2014")
filename
```

Loading the data set for the given year is provided by the `fars_read` function:

```{r}
df <- fars_read(fars_example("accident_2013.csv.bz2"))
head(df)
```

The `fars` package also provides basic analysis functions:

```{r eval=FALSE}
fars_summarize_years(2014)
```

As well as the possibility to plot the accidents per state for a given year:

```{r eval=FALSE}
fars_map_state(5, 2014)
```
